\documentclass[12pt]{article}
\usepackage{amsmath}

\begin{document}
\section{Q1}
\subsection{a}
Probability distribution of x and y, use 
\begin{equation}
	P(x) = \sum_i \frac{p(g_i(x))}{| f'(g_i(x)) |}
\end{equation}
We have $x=f(\phi) = a\cos\phi$, $g_1(x) = \arccos(\frac{x}{a})$, 
$g_2(x) =2\pi- \arccos(\frac{x}{a})$, $|f'(\phi)|=|a\sin\phi|= |a\sqrt{1-\cos^2\phi}|$ 
So:
\begin{equation}
	P(x) = \frac{1}{\pi\sqrt{a^2-x^2}}
\end{equation}
And the same for $P_x(x) = P_y(y)$ from symmetry.
\subsection{b}
For the join probability distribution, we can use 
\begin{equation}
	p(x, y) = \mathcal{P}(x|y)p(y)
\end{equation}
Where $\mathcal{P}(x|y)=\frac{1}{2}\delta(x^2+y^2-a^2)$, so:
\begin{equation}
	p(x, y) = \frac{\delta(x^2+y^2-a^2)}{2\pi\sqrt{(a^2-y^2)}}
\end{equation}
\subsection{c}
The covariance of x and y is: $\left<\Delta x \Delta y\right>=\left<(x-\left<x\right>)(y-\left<y\right>)\right>=\left<xy\right>-\left<x\right>\left<y\right>$ Which is zero because the probability distribution $p(x)$ is even.
\\
The distributions are statistically dependent since $p(x, y)\neq p(x)p(y)$.
\section{Q2}
The characteristic function of the random variable $x$ is:

\begin{equation}
	C(\xi) = 
	\begin{cases}
		\frac{b+\xi}{b-a} & -b<\xi\leq-a \\
		1 & a-<\xi\leq a\\
		\frac{b-\xi}{b-a} & a<\xi\leq b \\
		0 & \text{Otherwise}
	\end{cases}
\end{equation}
Can get the probability distribution as the fourier transform of this:
\begin{equation}
	p(x) = \frac{1}{2\pi}\int e^{-i\xi x}C(\xi)d\xi
\end{equation}
Since $C(\xi)$ is even, only the even part of the exponential contributes, so we need to perform the integral:
\begin{equation}
	p(x) = \frac{1}{2\pi}\int_{-b}^b C(\xi)\cos(x\xi)d\xi
\end{equation}
Perform the integral over the 3 parts, giving:
\begin{equation}
	p(x) = \frac{\cos(ax)-\cos(bx)}{\pi(b-a)x^2}
\end{equation}
\section{Q3}
Probability of $m$ failures and $n$ successes, with last trial ending in success. Probability of a success is $\alpha$.
\begin{equation}
	p(m, n) = \left(\begin{matrix}m+n-1\\m\end{matrix}\right)(1-\alpha)^m\alpha^n
\end{equation}
The r'th factorial moment of $m$ for fixed $n$ is
\begin{align*}
	\left<m^{(r)}\right>=\frac{d^r}{d\xi^r}\left<(1+\xi)^m\right>\Big |_{\xi=0} \\
			    =\frac{d^r}{d\xi^r}\sum_{m=0}^\infty (1+\xi)^m \left(\begin{matrix}m+n-1\\m\end{matrix}\right)(1-\alpha)^m\alpha^n\Big|_{\xi=0} \\
			    =\alpha^n\frac{d^r}{d\xi^r}\sum_{m=0}^\infty\left(\begin{matrix}-n\\m\end{matrix}\right)(\alpha-1+\alpha\xi-\xi)^m\Big|_{\xi=0} \\
			    =\alpha^n \frac{d^r}{d\xi^r}(\alpha+\alpha\xi-\xi)^{-n}\Big|_{\xi=0} \\
			    =\alpha^n (1-\alpha)^r\alpha^{1-n-r}\frac{(n+r-1)!}{(n-1)!} \\
			    =\alpha^{1-r}(1-\alpha)^r\frac{(n+r-1)!}{(n-1)!}
\end{align*}
Where from the 3rd to the 4th line the binomial expansion is used.
\end{document}
